4-examples

### 2022-06-16 4-1-basic.Rmd
Update section 4-1

The six examples here are chosen to illustrate creating a cubble for exploring COVID data where id's need to be matched, using spatial transformations to make a glyph map of seasonal temperature changes over years, aggregating information spatially to explore precipitation patterns, matching river level data and weather station records for analysis of water supply, reading netCDF format data to reproduce a climate reanalysis plot, and the workflow to create complex interactive linked plots.

@@

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{weatherdata::historical_tmax} is a subset containing the records of maximum temperature for `r nrow(weatherdata::historical_tmax)` Australian stations `r range(weatherdata::historical_tmax$first_year)[2]` through `r range(weatherdata::historical_tmax$first_year)[2]`.  and provides information also on the latitude, longitude and elevation of each of the  stations. This **cubble** data  is already cast into a \code{cubble} data object, with \code{id} as the key, \code{date} as the index, and \code{c(longitude, latitude)} as the coordinates. The goal of this example is to compare the monthly average maximum temperature  between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.

>>>>

The six examples here are chosen to illustrate creating a cubble for exploring COVID data where location identities need to be matched, using spatial transformations to make a glyph map of seasonal temperature changes over years, aggregating information spatially to explore precipitation patterns, matching river level data and weather station records for analysis of water supply, reading netCDF format data to reproduce a climate reanalysis plot, and the workflow to create complex interactive linked plots.

@@

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{weatherdata::historical_tmax} is a subset containing the records of maximum temperature for `r nrow(weatherdata::historical_tmax)` Australian stations `r from range(weatherdata::historical_tmax$first_year)[1]` through `r range(weatherdata::historical_tmax$first_year)[2]` and provides information also on the latitude, longitude and elevation of each of the  stations. This data  is already cast into a \code{cubble} data object (please see Appendix X for the code to extract  the data from XX and prepare the data into \code{cubble} form), with \code{id} as the key, \code{date} as the index, and \code{c(longitude, latitude)} as the coordinates. The goal of this example is to compare the monthly average maximum temperature  between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.
